\documentclass[a4paper,12pt]{article}

\usepackage[unicode,colorlinks=true,linkcolor=blue]{hyperref}
\usepackage{amsmath,amssymb}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[russian]{babel}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{enumerate}
\usepackage{minted}

\pagestyle{fancy}
\makeatletter
\fancyhead[L]{\footnotesize BS3-5, 2015, <<DMD>>}
\fancyfoot[L]{\footnotesize \@author}
\fancyfoot[R]{\thepage}
\fancyfoot[C]{}

\renewcommand{\maketitle}{%
\noindent{\bfseries\scshape\large\@title\ \mdseries\upshape(\@date)}\par
\noindent {\large\itshape\@author}
\vskip 2ex}
\makeatother

\newenvironment{problem}[1]{\par\bigskip\noindent\textbf{Problem #1.}
  \enskip\ignorespaces}{}

\title{DMD homework 7} % Fill the number of the homework
\author{Tropin Andrew \\
  e-mail: \href{mailto:andrewtropin@gmail.com}{andrewtropin@gmail.com} \\
  github: \href{http://github.com/abcdw}{abcdw}}
\date{\today} % Fill the date

\begin{document}
  \maketitle
  \thispagestyle{fancy}

  \begin{problem}{1}
    \inputminted{sql}{./1.sql}
    \begin{enumerate}
      \item Complicated where condition, because of many Title columns.
      \item Nope, because we can't simply use COUNT function.
    \end{enumerate}
  \end{problem}

  \begin{problem}{2}
    \begin{enumerate}
      \item Add more columns with titles.
      \item Add rows with same RentalID, CustID and different titles and nulls
        for empty columns.
    \end{enumerate}
  \end{problem}

  \begin{problem}{3}
    (\underline{RentalID}, CustID, CheckOutDate, \underline{Title}) \\
    PK highlighted with underline.
  \end{problem}

  \begin{problem}{4}
    \inputminted{sql}{./2.sql}
  \end{problem}

  \begin{problem}{5}
    \inputminted{sql}{./3.sql}
  \end{problem}

  \begin{problem}{6}
    \inputminted{sql}{./4.sql}
  \end{problem}

  \begin{problem}{7}
    \begin{itemize}
      \item $RentalID \rightarrow CustID$
      \item $RentalID \rightarrow CheckOutDate$
      \item $RentalID \rightarrow ReleaseType$
      \item $Title \rightarrow Director$
      \item $ReleaseType \rightarrow Price$
    \end{itemize}
  \end{problem}

  \begin{problem}{8}
    We have FDs with left-side attribute, that doesn't belongs to key.
  \end{problem}

  \begin{problem}{9}
    \begin{itemize}
      \item We don't reuse already existing information. For example, we have
        two rows with informaiton about film ``Die Hard'' and it's Director.
        And every time, when we add rental information about same film, we
        need to write all information about film, that already exists in
        other row.
      \item We lose information about film, when all rows related to this
        film were deleted.
      \item We need to change many tuples, when we want change informaiton
        about one film. For example, with FK it's necessary to change only
        one row.
    \end{itemize}
  \end{problem}

  \begin{problem}{10}
    \begin{itemize}
      \item (\underline{RentalID}, \underline{Title}, CustID, CheckOutDate, ReleaseType)
      \item (\underline{Title}, Director)
      \item (\underline{ReleaseType}, Price)
    \end{itemize}
  \end{problem}

  \begin{problem}{11}
    Multivalued dependency. In that table we have two Multivalued dependencies:
    \begin{itemize}
      \item Course to Teacher
      \item Course to Book
    \end{itemize}
    When we want to add Book to Course it's necessary to add that book
    for every teacher on that course.
  \end{problem}

  \begin{problem}{12}
    No.
  \end{problem}

  \begin{problem}{13}
    It's necessary to create two relations (Course, Teacher) and (Course, Book).
  \end{problem}

  \begin{problem}{14}
    No. FD $City, State \rightarrow ZipCode$ has not key left-side attribute.
  \end{problem}

  \begin{problem}{15}
    I wouldn't. Because it's too complicated for such small dataset.
  \end{problem}

\end{document}
