\documentclass[a4paper,12pt]{article}

\usepackage[unicode,colorlinks=true,linkcolor=blue]{hyperref}
\usepackage{amsmath,amssymb}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[russian]{babel}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{minted}

\pagestyle{fancy}
\makeatletter
\fancyhead[L]{\footnotesize BS3-5, 2015, <<OOP>>}
\fancyfoot[L]{\footnotesize \@author}
\fancyfoot[R]{\thepage}
\fancyfoot[C]{}

\renewcommand{\maketitle}{%
\noindent{\bfseries\scshape\large\@title\ \mdseries\upshape(\@date)}\par
\noindent {\large\itshape\@author}
\vskip 2ex}
\makeatother

\newenvironment{problem}[1]{\par\bigskip\noindent\textbf{Problem #1.}
  \enskip\ignorespaces}{}

\title{OOP homework 4} % Fill the number of the homework
\author{Tropin Andrew \\
  e-mail: \href{mailto:andrewtropin@gmail.com}{andrewtropin@gmail.com} \\
  github: \href{http://github.com/abcdw}{abcdw}}
\date{\today} % Fill the date

\begin{document}
  \maketitle
  \thispagestyle{fancy}

  \begin{problem}{1}
    Class is a description of set of objects with similiar properties. \\
    Class like a baking pan and object like a pie, baked with that pan.
  \end{problem}

  \begin{problem}{2}
    \begin{itemize}
      \item STRING\_8
      \item REAL\_64
      \item REAL\_64
    \end{itemize}

    Queries:
    \begin{itemize}
      \item Zurich.line(13).color.brightness
      \item Zurich.line(31).stations.at(3).item.position.y
      \item Zurich.line(31).next.station(Zurich.station(``Loewenplatz''),
        Zurich.line(31).west\_terminal)
      \item Zurich.station("Paradeplatz").lines.count
      \item Zurich.connecting\_lines(Zurich.station(``Paradeplatz''),
        Zurich.station(``Rennweg'')).has(Zurich.line(7))
    \end{itemize}

  \end{problem}

  \begin{problem}{3}
    \begin{minted}
class
	BUSINESS_CARD

create
	fill_in

feature {NONE} -- Initialization

	fill_in
			-- Fill in the card and print it.
		do
			io.put_string ("Your name:")
            io.read_line
			set_name(io.last_string)
			io.put_string ("Your job:")
			io.read_line
			set_job(io.last_string)
			io.put_string ("Your age:")
			io.read_integer
			set_age(io.last_integer)
			print_card
		end

feature -- Access

	name: STRING
			-- Owner's name.

	job: STRING
			-- Owner's job.

	age: INTEGER
			-- Owner's age.

feature -- Setting

	set_name (a_name: STRING)
			-- Set `name' to `a_name'.
		require
			name_exists: a_name /= Void
		do
			name := a_name.twin
		end

	set_job (a_job: STRING)
			-- Set `job' to `a_job'.
		require
			job_exists: a_job /= Void
		do
			job := a_job.twin
		end

	set_age (a_age: INTEGER)
			-- Set `age' to `a_age'.
		require
			age_non_negative: a_age >= 0
		do
			age := a_age
		end

feature -- Output
	age_info: STRING
			-- Text representation of age on the card.
		do
			Result := age.out + " years old"
		end

	Width: INTEGER = 50
			-- Width of the card (in characters), excluding borders.

	line (n: INTEGER): STRING
			-- Horizontal line on length `n'.
		do
			Result := "#"
			Result.multiply (n)
		end

	spaces (n: INTEGER): STRING
			-- Spaces in card
		do
			Result := " "
			Result.multiply (Width - n - 2)
		end

	print_card
			-- Printing card
		do
			io.put_string(line (Width))
			io.put_new_line
			io.put_string ("#" + name.out + spaces(name.count) + "#")
			io.put_new_line
			io.put_string ("#" + job.out + spaces(job.count) + "#")
			io.put_new_line
			io.put_string ("#" + age_info + spaces(age_info.count) + "#")
			io.put_new_line
			io.put_string(line(Width))

		end


end
    \end{minted}
  \end{problem}

  \begin{problem}{4}
    You can find me. Andrew Tropin.
  \end{problem}
\end{document}
